---
output: 
  github_document:
    toc: false
    fig_width: 10.08
    fig_height: 6
tags: [r, reports]
vignette: >
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

# Calendar

```{r, echo = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  dpi = 600,
  collapse = TRUE,
  fig.path = ""
)
options(knitr.kable.NA = '',
        digits = 4,
        width=60)


# Dependencies
library(chillR)
library(lunar)
library(fmdates)
```

```{r astromical_events, echo = FALSE}
source("https://raw.githubusercontent.com/RealityBending/scripts/main/astronomical_dates.R")
```

```{r dates_celebrations, echo = FALSE}
get_dates_celebrations <- function(year=2024){
  
  # Convenience function to find the midpoint between two dates
  midpoint <- function(date1, date2){
    days <- seq(date1, date2, by="days")
    days[round(length(days) / 2)]
  }
  
  # Get dates (latitude in Brightonn UK)
  astro_prev <- astronomical_dates(year=year-1, latitude = 50.8229)
  astro <- astronomical_dates(year=year, latitude = 50.8229)
  astro_next <- astronomical_dates(year=year+1, latitude = 50.8229)

  # Solar
  out <- c(
    "Preparationday"=midpoint(astro_prev$Solstice_Winter, astro$Equinox_Spring),  
    "Risefest"=astro$Equinox_Spring, 
    "Flowerday"=midpoint(astro$Equinox_Spring, astro$Solstice_Summer),
    "Lightfest"=astro$Solstice_Summer,
    "Harvestday"=midpoint(astro$Solstice_Summer, astro$Equinox_Autumn),
    "Fallfest"=astro$Equinox_Autumn,  
    "Rootday"=midpoint(astro$Equinox_Autumn, astro$Solstice_Winter),
    "Nightfest"=astro$Solstice_Winter  
    )
  
  # Lunar
  out <- c(
    out,
    "Winenight"=max(astro$Moon_Full[out["Preparationday"]-astro$Moon_Full > 0]), # Before Preparationday,
    "Innocentnight"=max(astro$Moon_Full[out["Risefest"]-astro$Moon_Full > 0]), # Before Risefest,
    "Deadsnight"=max(astro$Moon_Full[out["Rootday"]-astro$Moon_Full > 0]), # Before Nightfest
    "Loversnight"=astro$Moon_Full[which.min(abs(out["Flowerday"]-astro$Moon_Full))],  # Closest to Flowerday
    "Blacksun"=max(astro$Moon_Full[out["Nightfest"]-astro$Moon_Full > 0]) # Before Nightfest
    )
  
  # Other
  # blacksun_dates <- out["Nightfest"]-(7:14)
  # out <- c(out,
  #          "Blacksun" = blacksun_dates[weekdays(blacksun_dates) == "Friday"]
  # )
}
```

```{r find_closest, echo = FALSE}
get_dates <- function(){
  today <- Sys.Date()
  year <- as.numeric(format(today, "%Y"))
  
  dates <- as.Date(c())
  for(y in c(year, year + 1)){
    dates <- c(dates, get_dates_celebrations(y))
    d <- today - dates
    dates <- dates[d <= 0]
  }
  
  d <- today - dates
  next_date <- which.max(d)
  celeb <- names(next_date)
  
  if (celeb %in% c("Fallfest", "Harvestday")){
    season <- "Summer"
    period <- "Bright Days"
    phase <- "Fall"
  } else if (celeb %in% c("Rootday", "Deadsnight", "Nightfest")){
    season <- "Autumn"
    period <- "Dark Nights"
    phase <- "Fall"
  } else if (celeb %in% c("Winenight", "Risefest", "Preparationday")){
    season <- "Winter"
    period <- "Dark Nights"
    phase <- "Rise"
  } else if (celeb %in% c("Loversnight", "Lifesday", "Flowerday", "Lightfest")){
    season <- "Spring"
    period <- "Bright Days"
    phase <- "Rise"
  } else{
    season <- "FAILURE"
    period <- "FAILURE"
    phase <- "FAILURE"
  }
  
  # Celebrations
  list("N_Days" = abs(as.numeric(d[next_date])),
       "Next_Celebration" = celeb,
       "Season" = season,
       "Period" = period,
       "Phase" = phase)
}
```


```{r print, echo = FALSE, results='asis', message=FALSE, warning=FALSE}
info <- get_dates()

cat(paste0("We are in **",
           info$Season,
           "**. The **",
           info$Period,
           "** are upon us, and we are in the time of the **",
           info$Phase,
           "**. ",
           "The next celebration is [**", 
           info$Next_Celebration, 
           "**](https://github.com/RealityBending/Calendar#", 
           info$Next_Celebration, 
           ") in **", 
           info$N_Days, 
           "** days",
           ifelse(info$N_Days == 14, " (@DominiqueMakowski).", ".")))
```



## Celebrations


```{r calendar_plot, echo=FALSE, message=FALSE, warning=FALSE, dpi=450}
library(ggplot2)

year <- as.numeric(format(Sys.Date(), "%Y"))
days <- as.Date(seq(ISOdate(year, 1, 1), ISOdate(year, 12, 31), by='day'))
celebrations <- get_dates_celebrations(year)

# Create data
data <- data.frame(Day = days,
                   Celebration = NA,
                   Main = NA,
                   Type = ifelse(days %in% celebrations[c("Risefest", "Fallfest", "Nightfest", "Lightfest",
                                                           "Preparationday", "Flowerday", "Rootday", "Harvestday")], "Solar", "Lunar"))

for(i in 1:length(celebrations)) {
  if(is.na(data[data$Day == celebrations[i], "Celebration"])){
    data[data$Day == celebrations[i], "Celebration"] <- names(celebrations[i])
  } else{
    data[data$Day == celebrations[i], "Celebration"] <- paste(data[data$Day == celebrations[i], "Celebration"], "/", names(celebrations[i]))
  }
}

data$Bar <- ifelse(is.na(data$Celebration), 0, 1)
data$Width <- NA
data$Width[data$Celebration %in% c("Nightfest", "Risefest", "Lightfest", "Fallfest")] <- 2
data$Width[data$Celebration %in% c("Preparationday", "Flowerday", "Harvestday", "Rootday")] <- 1
data$Width[data$Celebration %in% c("Winenight", "Innocentnight", "Loversnight", 
                                   "Deadsnight", "Blacksun")] <- 1.5



# data$Bar[data$Type == "Solar" & data$Main == 0.5] <- 0
data$Bar[data$Type == "Lunar"] <- 0.9
data$Bar[data$Type == "Other"] <- 0.8

data_segments <- data[!is.na(data$Celebration) & data$Type == "Solar", ]
segments <- data.frame(
  Day = data_segments$Day[data_segments$Celebration %in% c("Risefest", "Lightfest", "Fallfest")],
  xend = data_segments$Day[data_segments$Celebration %in% c("Flowerday", "Harvestday", "Rootday")],
  y = 1)
# Add around beginning of year
segments <- rbind(segments, 
                  data.frame(Day=data_segments$Day[8], xend=max(data$Day), y=1),
                  data.frame(Day=min(data$Day),  xend=data_segments$Day[1], y=1))




ggplot(data, aes(x = Day, y=Bar)) +
  geom_bar(aes(fill=Type), width=data$Width, stat = "identity", position="identity") +
  geom_segment(data = segments, aes(xend = xend, y = y, yend = y), color = "#f44336", linewidth = 2) +
  geom_bar(data=data.frame(Day = Sys.Date(), Bar=0.8), fill="black", width=3, stat = "identity", position="identity") +
  geom_text(aes(label=Celebration), y=1.25, size = 3, angle = 0, fontface="italic") +
  coord_polar(start=0, clip = "off") +
  theme_void() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(face= "bold"),
        axis.ticks.y = element_blank(),
        axis.line.x = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        panel.grid.major.y = element_blank(), 
        panel.grid.major =  element_line(colour = "#FFB300")) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1), breaks = NULL) +
  guides(fill="none") +
  scale_x_date(date_breaks = "1 month", 
               date_labels = month.abb, 
               limits = range(c(days[1], days[-1]))) +
  scale_fill_manual(values=c("Lunar"="#2196F3", "Solar"= "#f44336", "Other"="purple"))
```

In the Reality Bending Lab, we follow an astronomical calendar. The year is divided in two main overlapping cycles, the **Rise/Fall** phases (December - June) and the **Dark nights/Bright days** periods (September - March). 

*Note: this calendar is automatically updated daily thanks to an automated R script that accounts for the exact dates of the solar and lunar astronomical events (solstices, equinoxes, full moons) of the current year.*


### Winenight

**Fullmoon before Preparationday** `r format(celebrations["Winenight"], "*(%Y %B %d - %A)*")`. Wine drinking. (See [Anthesteria](https://en.wikipedia.org/wiki/Anthesteria)).

### Preparationday

**Between Nightfest and Risefest** `r format(celebrations["Preparationday"], "*(%Y %B %d - %A)*")`. Ploughing and Sowing. Team building and planning of the work roadmap for the year. (See [Imbolc](https://en.wikipedia.org/wiki/Imbolc)).

### Festival of the Innocents

**Fullmoon before Preparationday** `r format(celebrations["Innocentfest"], "*(%Y %B %d - %A)*")`. Masked party. Anonymity and roles. Wolves and sheep. Winter retreat. (See [Lupercalia](https://en.wikipedia.org/wiki/Lupercalia) and [Carnival of Venice](https://en.wikipedia.org/wiki/Carnival_of_Venice)).


### Risefest

**Spring equinox** `r format(celebrations["Risefest"], "*(%Y %B %d - %A)*")`. Coming of **Bright days** and **Spring**. Drowning of the *Winter Woman* (See [Marzanna](https://wpna.fm/polish-traditions-the-drowning-of-marzanna/)). Eating eggs and water pranks.

### Loversnight

**Fullmoon between Risefest and Lightfest** `r format(celebrations["Loversnight"], "*(%Y %B %d - %A night)*")`. Celebration of partners and loved ones. (see [Walpurgis' Night](https://en.wikipedia.org/wiki/Walpurgis_Night) and [Beltane](https://en.wikipedia.org/wiki/Beltane))

### Flowerday

**Between Risefest and Lightfest** `r format(celebrations["Flowerday"], "*(%Y %B %d - %A)*")`. Celebration of life, youth and growth. Flowers in bloom and celebrations around the tree. (See [Floria](https://en.wikipedia.org/wiki/Floralia) and [May Day](https://en.wikipedia.org/wiki/May_Day)).

### Lightfest

**Summer solstice** `r format(celebrations["Lightfest"], "*(%Y %B %d - %A)*")`. Crackers and fireworks at sunset. Popcorns made in fires in the night. (See [Kupala Night](https://en.wikipedia.org/wiki/Kupala_Night)).

### Harvestday

**Between Lightfest and Fallfest** `r format(celebrations["Harvestday"], "*(%Y %B %d - %A)*")`. We harvest the fruits of our work and relax. Work superiors treat to dinner. Rewards and vacations. Start of summer break. (See [Lughnasadh](https://en.wikipedia.org/wiki/Lughnasadh)).  


### Fallfest

**Autumn equinox** `r format(celebrations["Fallfest"], "*(%Y %B %d - %A)*")`. 
Coming of the **Dark Nights** and **Autumn**. Beginning of the school year.
Fires are lit (no electricity). [Wreaths](https://en.wikipedia.org/wiki/Do%C5%BCynki) symbolizing the successful readiness for the year to come. We go on a walk and collect materials to create along the way the *Winter Woman* doll, that will stay in the lab until Risefest. Followed by a feast. (See [Oktoberfest](https://en.wikipedia.org/wiki/Oktoberfest) and [Thanksgiving](https://en.wikipedia.org/wiki/Thanksgiving)).

### Deadsnight

**Fullmoon before Rootday** `r format(celebrations["Deadsnight"], "*(%Y %B %d - %A)*")`. Visit cemeteries. (See [Samhain](https://en.wikipedia.org/wiki/Samhain), [Halloween](https://en.wikipedia.org/wiki/Halloween)).

### Rootday

**Between Fallfest and Nightfest** `r format(celebrations["Rootday"], "*(%Y %B %d - %A)*")`. Nature is withering, and we prepare for the cold. Celebrate our roots and ancestors. Cultural and historical activities. 

### Blacksun

- **Fullmoon before Nightfest** `r format(celebrations["Blacksun"], "*(%Y %B %d - %A)*")`. When darkness is winning: Chaos and mischief. Elect a "Lord of Misrule". Inversed hierarchy (see [Saturnalia](https://en.wikipedia.org/wiki/Saturnalia)).

### Nightfest

**Winter solstice** `r format(celebrations["Nightfest"], "*(%Y %B %d - %A)*")`. From that date until the 6th of January, people keep a tree inside of their houses. On the 21th, it is decorated with garlands, and people drink snake wine.


### Other (to be done)

- Move Loversnight to be consistently before/after FLowerday?
