---
output: 
  github_document:
    toc: false
    fig_width: 10.08
    fig_height: 6
tags: [r, reports]
vignette: >
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

# Calendar

```{r, echo = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  dpi = 600,
  collapse = TRUE,
  fig.path = ""
)
options(knitr.kable.NA = '',
        digits = 4,
        width=60)


# Dependencies
library(chillR)
library(lunar)
library(fmdates)
```

```{r astromical_events, echo = FALSE}
# Define convenience function (needs to 'chillR' and the 'lunar' package) to find dates of solstices, equinoxes, full moons and new moons for a given year.
get_dates_atronomical <- function(year=2023){
  dates <- seq(ISOdate(year, 1, 1), ISOdate(year, 12, 31), by='day')
  days <- chillR::make_JDay(data.frame(Year=format(dates, "%Y"),Month=format(dates, "%m"),Day=format(dates, "%d")))
  daylength <- chillR::daylength(latitude = 50.8229, days$JDay)$Daylength  # Latitude in Brighton, UK

  # Solstice
  solstice_winter <- as.Date(dates[which(daylength==min(daylength))])
  solstice_summer <- as.Date(dates[which(daylength==max(daylength))])
  
  # Equinox
  equinox_spring <- as.Date(fmdates:::equinox(year, season = "mar", tz = "GMT"))
  equinox_autumn <- as.Date(fmdates:::equinox(year, season = "sep", tz = "GMT"))
  
  # Full moons
  phase <- lunar::lunar.illumination(dates)
  moon <- data.frame(dates = as.Date(dates), 
                     phase = phase,
                     newmoon = FALSE,
                     fullmoon = FALSE)
  moon[which(diff(sign(diff(phase)))==-2)+1, "fullmoon"] <- TRUE 
  moon[which(diff(sign(diff(phase)))==2)+2, "newmoon"] <- TRUE 
  
  list("Solstice_Summer"=solstice_summer, 
       "Solstice_Winter"=solstice_winter,
       "Equinox_Autumn"=equinox_autumn, 
       "Equinox_Spring"=equinox_spring,
       "Moon_Full"=moon[moon$fullmoon==TRUE, "dates"],
       "Moon_New"=moon[moon$newmoon==TRUE, "dates"],
       "Dates"=dates)
}
```

```{r dates_celebrations, echo = FALSE}
get_dates_celebrations <- function(year=2024){
  
  # Convenience function to find the midpoint between two dates
  midpoint <- function(date1, date2){
    days <- seq(date1, date2, by="days")
    days[round(length(days) / 2)]
  }
  
  # Get dates
  astro_prev <- get_dates_atronomical(year=year-1)
  astro <- get_dates_atronomical(year=year)
  astro_next <- get_dates_atronomical(year=year+1)

  # Solar
  out <- c(
    "Darkrise"=midpoint(astro_prev$Solstice_Winter, astro$Equinox_Spring),
    "Sunfest"=astro$Equinox_Spring,
    "Brightrise"=midpoint(astro$Equinox_Spring, astro$Solstice_Summer),
    "Fallfest"=astro$Solstice_Summer,
    "Brightfall"=midpoint(astro$Solstice_Summer, astro$Equinox_Autumn),
    "Moonfest"=astro$Equinox_Autumn,
    "Darkfall"=midpoint(astro$Equinox_Autumn, astro$Solstice_Winter),
    "Risefest"=astro$Solstice_Winter
    )
  
  # Lunar
  fullmoon_darkfall <- astro$Moon_Full[which.min(abs(out["Darkfall"]-astro$Moon_Full))]
  fullmoon_darkrise <- astro$Moon_Full[which.min(abs(out["Darkrise"]-astro$Moon_Full))]
  
  c(
    out,
    "Thanksday"=astro$Moon_Full[which.min(abs(out["Brightfall"]-astro$Moon_Full))],
    "Harvestday"=fullmoon_darkfall,
    "Deadsnight"=fullmoon_darkfall,
    "Preparationday"=fullmoon_darkrise,
    "Loversnight"=astro$Moon_Full[which.min(abs(out["Brightrise"]-astro$Moon_Full))],
    "Lifesday"=astro$Moon_Full[which.min(abs(out["Brightrise"]-astro$Moon_Full))]
    )
  
}
```

```{r find_closest, echo = FALSE}
get_dates <- function(){
  today <- Sys.Date()
  year <- as.numeric(format(today, "%Y"))
  
  dates <- as.Date(c())
  for(y in c(year, year + 1)){
    dates <- c(dates, get_dates_celebrations(y))
    d <- today - dates
    dates <- dates[d <= 0]
  }
  
  d <- today - dates
  next_date <- which.max(d)
  celeb <- names(next_date)
  
  if (celeb %in% c("Thanksday", "Moonfest", "Brightfall")){
    season <- "Summer"
    period <- "Bright Days"
    phase <- "Fall"
  } else if (celeb %in% c("Harvestday", "Deadsnight", "Darkfall")){
    season <- "Autumn"
    period <- "Dark Nights"
    phase <- "Fall"
  } else if (celeb %in% c("Risefest")){
    season <- "Winter"
    period <- "Dark Nights"
    phase <- "Fall"
  } else if (celeb %in% c("Preparationday", "Sunfest", "Darkrise")){
    season <- "Winter"
    period <- "Dark Nights"
    phase <- "Rise"
  } else if (celeb %in% c("Loversnight", "Lifesday", "Brightrise")){
    season <- "Spring"
    period <- "Bright Days"
    phase <- "Rise"
  } else if (celeb %in% c("Fallfest")){
    season <- "Summer"
    period <- "Bright Days"
    phase <- "Rise"
  } else{
    season <- "FAILURE"
    period <- "FAILURE"
    phase <- "FAILURE"
  }
  
  # Celebrations
  list("N_Days" = abs(as.numeric(d[next_date])),
       "Next_Celebration" = celeb,
       "Season" = season,
       "Period" = period,
       "Phase" = phase)
}
```


```{r print, echo = FALSE, results='asis', message=FALSE, warning=FALSE}
info <- get_dates()

cat(paste0("We are in **",
           info$Season,
           "**. The **",
           info$Period,
           "** are upon us, and we are in the time of the **",
           info$Phase,
           "**. ",
           "The next celebration is [**", 
           info$Next_Celebration, 
           "**](https://github.com/RealityBending/Calendar#", 
           info$Next_Celebration, 
           ") in **", 
           info$N_Days, 
           "** days",
           ifelse(info$N_Days == 10, " (@DominiqueMakowski).", ".")))
```


## Important dates

None yet.

## Celebrations


```{r calendar_plot, echo=FALSE, message=FALSE, warning=FALSE, dpi=450}
library(ggplot2)

year <- as.numeric(format(Sys.Date(), "%Y"))
days <- as.Date(seq(ISOdate(year, 1, 1), ISOdate(year, 12, 31), by='day'))
celebrations <- get_dates_celebrations(year)

# Create data
data <- data.frame(Day = days,
                   Celebration = NA,
                   Main = NA,
                   Type = ifelse(days %in% celebrations[c("Sunfest", "Moonfest", "Risefest", "Fallfest",
                                                           "Darkrise", "Brightrise", "Darkfall", "Brightfall")], "Solar", "Lunar"))

for(i in 1:length(celebrations)) {
  if(is.na(data[data$Day == celebrations[i], "Celebration"])){
    data[data$Day == celebrations[i], "Celebration"] <- names(celebrations[i])
  } else{
    data[data$Day == celebrations[i], "Celebration"] <- paste(data[data$Day == celebrations[i], "Celebration"], "/", names(celebrations[i]))
  }
}

data$Bar <- ifelse(is.na(data$Celebration), 0, 1)
data$Main <- ifelse(data$Day %in% celebrations[c("Sunfest", "Moonfest", "Risefest", "Fallfest",
                                                 "Harvestday", "Preparationday", "Thanksday", "Loversnight")], 2, ifelse(is.na(data$Celebration), NA, 0.5))


ggplot(data, aes(x = Day, y=Bar)) +
  geom_bar(aes(fill=Type), width=data$Main, stat = "identity", position="identity") +
  geom_bar(data=data.frame(Day = Sys.Date(), Bar=0.8), fill="black", width=3, stat = "identity", position="identity") +
  geom_text(aes(label=Celebration), y=1.1, size = 3, angle = 0, fontface="italic") +
  coord_polar(start=0) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major =  element_line(colour = "#B0BEC5")) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1), breaks = NULL) +
  guides(fill=FALSE) +
  scale_x_date(date_breaks = "1 month", date_labels = month.abb, limits = range(c(days[1], days[-1]))) +
  scale_fill_manual(values=c("Lunar"="#2196F3", "Solar"= "#f44336"))
```

In the Reality Bending Lab, we follow an astronomical calendar. The year is divided in two main overlapping cycles, the **Rise/Fall** phases (December - June) and the **Dark nights/Bright days** periods (September - March). 

*Note: this calendar is automatically updated daily, taking into account the exact dates of the solar and lunar astronomical events (solstices, equinoxes, full moons) of the current year.*


### Preparationday

**Fullmoon between Risefest and Sunfest** `r format(celebrations["Preparationday"], "*(%Y %B %d - %A)*")`. Team building and planning of the work roadmap for the year.

### Sunfest

**Spring equinox** `r format(celebrations["Sunfest"], "*(%Y %B %d - %A)*")`. Eating eggs and water pranks. Coming of **Bright days** and **Spring**.

### Loversnight

**Fullmoon between Sunfest and Fallfest** `r format(celebrations["Loversnight"], "*(%Y %B %d - %A night)*")`. Celebration of partners and loved ones.

### Lifesday

**Day after Loversnight** `r format(celebrations["Loversnight"] + 1, "*(%Y %B %d - %A)*")`. Visit to parents and family. Start of **Summer**.

### Fallfest

**Summer solstice** `r format(celebrations["Fallfest"], "*(%Y %B %d - %A)*")`. Crackers and fireworks at sunset. Popcorns made in fires in the night.

### Thanksday

**Fullmoon between Fallfest and Moonfest** `r format(celebrations["Thanksday"], "*(%Y %B %d - %A)*")`. Work superiors treat to dinner. Rewards and vacations.

### Moonfest

**Autumn equinox** `r format(celebrations["Moonfest"], "*(%Y %B %d - %A)*")`. Fires are lit (no electricity). Coming of the **Dark Nights** and **Autumn**.

### Harvestday

**Day before the fullmoon between Moonfest and Risefest** `r format(celebrations["Harvestday"], "*(%Y %B %d - %A)*")`. Physical/sport games and competitions between colleagues.

### Deadsnight

**Fullmoon between Moonfest and Risefest** `r format(celebrations["Deadsnight"], "*(%Y %B %d - %A)*")`. Visit to cemeteries. Start of **Winter**.

### Risefest

**Winter solstice** `r format(celebrations["Risefest"], "*(%Y %B %d - %A)*")`. From that date until the 6th January, people keep a tree inside of their houses. On the 21th, it is decorated with garlands, and people drink snake wine.



